---
title: "ARIMA+GARCH Trading Strategy on the S&P500 Stock Market Index Using R"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
---

# Source

[ARIMA+GARCH Trading Strategy on the S&P500 Stock Market Index Using R](https://www.quantstart.com/articles/ARIMA-GARCH-Trading-Strategy-on-the-SP500-Stock-Market-Index-Using-R/)

# Libraries

```{r}
library(quantmod)
library(lattice)
library(timeSeries)
library(rugarch)

library(reticulate)
```


# Data

Get the differenced logarithmic return of the closing price of the S&P 500:

```{r}
getSymbols("^GSPC", from="2017-01-01", to="2021-05-02")
spReturns = diff(log(Cl(GSPC)))
spReturns[as.character(head(index(Cl(GSPC)),1))] = 0
```

A vector to store the forecast of each day:

```{r}
windowLength = 500
foreLength = length(spReturns) - windowLength
forecasts <- vector(mode="character", length=foreLength)
```

# Prediction

Loop through each each to generate predictions based on window of length `windowLength`:

```{r}
for (d in 0:foreLength) {
  # vector of returns to fit the model
  spReturnsOffset = spReturns[(1 + d):(windowLength + d)]
  
  final.aic <- Inf
  final.order <- c(0, 0, 0)
  
  # for ther arima model, set d = 0, and try p = 0..5
  # and q = 0..5 but never p = q = 0
  for (p in 0:5)
    for (q in 0:5) {
      if (p == 0 && q == 0) {
        next
      }
      
      # fit an arima model
      arimaFit = tryCatch(
        arima(spReturnsOffset, order = c(p, 0, q)),
        error = function(err)
          FALSE,
        warning = function(err)
          FALSE
      )
      
      # if have an arimafit, check if it has the best AIC
      if (!is.logical(arimaFit)) {
        current.aic <- AIC(arimaFit)
        if (current.aic < final.aic) {
          final.aic <- current.aic
          final.order <- c(p, 0, q)
          final.arima <-
            arima(spReturnsOffset, order = final.order)
        }
      } else {
        next
      }
    }
  
  # Specify and fit the GARCH(1,1) model
  spec = ugarchspec(
    variance.model = list(garchOrder = c(1, 1)),
    mean.model = list(
      armaOrder = c(final.order[1], final.order[3]),
      include.mean = T
    ),
    distribution.model = "sged"
  )
  
  fit = tryCatch(
    ugarchfit(spec, spReturnsOffset, solver = 'hybrid'),
    error = function(e)
      e,
    warning = function(w)
      w
  )
  
  # If we can't fit a model, predict "1"
  
  if (is(fit, "warning")) {
    forecasts[d + 1] = paste(index(spReturnsOffset[windowLength]), 1, sep =
                               ",")
    print(paste(index(spReturnsOffset[windowLength]), 1, sep = ","))
  } else {
    # otherwise, if forecasted return less than 0, return -1 else +1
    fore = ugarchforecast(fit, n.ahead = 1)
    ind = fore@forecast$seriesFor
    forecasts[d + 1] = paste(colnames(ind), ifelse(ind[1] < 0,-1, 1), sep =
                               ",")
    print(paste(colnames(ind), ifelse(ind[1] < 0,-1, 1), sep = ","))
  }
  
}
   
   
```
# Save the results

Save the forecast vector for further analysis.

Note: The full results from the article can be downloaded [here](https://s3.amazonaws.com/quantstartmedia/data/forecasts_new.csv).

```{r}
 write.csv(forecasts, file="forecasts_test.csv", row.names=FALSE)
```


Adjust the signal:


```{python}
forecasts = open("forecasts_test.csv", "r").readlines()

old_value = 1
new_list = []
for f in forecasts[1:]:
    strpf = f.replace('"','').strip()
    new_str = "%s,%s\n" % (strpf, old_value)
    newspl = new_str.strip().split(",")
    final_str = "%s,%s\n" % (newspl[0], newspl[2])
    final_str = final_str.replace('"','')
    old_value = f.strip().split(',')[1]
    new_list.append(final_str)

out = open("forecasts_new.csv", "w")
for n in new_list:
    out.write(n)
    
out.close()
```


# Analytics

Read the saved results:

```{r}

spArimaGarch = as.xts(read.zoo(
  file = "forecasts_new.csv",
  format = "%Y-%m-%d",
  header = F,
  sep = ","
))
```

Join the returns data:

```{r}
spIntersect = merge(spArimaGarch[, 1], spReturns, all = F)
spArimaGarchReturns = spIntersect[, 1] * spIntersect[, 2]
```

Buy and hold as a benchmark:

```{r}
spArimaGarchCurve = log(cumprod(1 + spArimaGarchReturns))
spBuyHoldCurve = log(cumprod(1 + spIntersect[, 2]))
spCombinedCurve = merge(spArimaGarchCurve, spBuyHoldCurve, all = F)
```

Visualize:

```{r}
xyplot(
  spCombinedCurve,
  superpose = T,
  col = c("darkred", "darkblue"),
  lwd = 2,
  key = list(text = list(c(
    "ARIMA+GARCH", "Buy & Hold"
  )),
  lines = list(
    lwd = 2, col = c("darkred", "darkblue")
  ))
)
```

