---
title: "ARIMA+GARCH Trading Strategy on the S&P500 Stock Market Index Using quantstrat"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
---

# Libraries

Load required libraries:

```{r echo = T, results = 'hide'}
library(tidyquant)
library(lattice)

library(timetk)
library(forecast)
library(rugarch)
library(broom)

library(quantstrat)
library(tidyverse)
```

Print some system info to help with reproducibility:

```{r}
sessionInfo()
```
# Data

Get data for the S&P 500 and compute its log returns:

```{r}
start_date <- "2017-01-01"
end_date <- "2021-05-02"
# end_date <- "2017-06-15"

stock_ticker <- "SPY"

df <-  tq_get(stock_ticker,
              get = "stock.prices",
              from = start_date,
              to = end_date) %>%
  tq_mutate(
    select = close,
    mutate_fun = dailyReturn,
    type = "log",
    col_rename = "daily_return"
  ) %>%
  select(-symbol)

df %>%
  head(5)
```

# Strategy Setup

Parameters related to the backtest:

```{r}
# window size to compute rolling ARIMA+GARCH indicator
window_size <- 500
# window_size <- 100

# date to start the backtest
init_date <- "2016-12-31"

# starting equity
init_equity <- 1e6

# total units per long/short position
max_position <- trunc(init_equity/(df %>% head(1) %>% pull(close)))

# units to long/short position
pos_per_signal <- trunc(max_position/2)
# pos_per_signal <- max_position
```

Parameters related to the security:

```{r}
currency("USD")
```

One way to get quantstrat access to the data is to assign it to the variable named as the ticker symbol in the global environment:

```{r}
df %>%
  # quantstrat expects data to be in xts
  tk_xts(date_var = date, select = -date) %>%
  assign(stock_ticker, ., envir = .GlobalEnv)
  
stock(stock_ticker, currency = "USD", multiplier = 1)

SPY %>%
  head(5)
```
Initialize some objects related to quantstrat:

```{r}
portfolio.st <- "Port.ARIMA+GARCH"
account.st <- "Acct.ARIMA+GARCH"
strategy.st <- "Strat.ARIMA+GARCH"

rm.strat(portfolio.st)
rm.strat(account.st)


initAcct(
  name = account.st,
  portfolios = portfolio.st,
  initDate = init_date,
  initEq = init_equity
)


initPortf(name = portfolio.st,
          symbols = stock_ticker,
          initDate = init_date)

addPosLimit(portfolio.st, stock_ticker, init_date, maxpos = max_position)


initOrders(portfolio = portfolio.st,
           symbols = stock_ticker,
           initDate = init_date)

strategy(strategy.st, store = TRUE)


```

# ARIMA+GARCH Indicator

Functions to help compute the ARIMA+GARCH indicator:

```{r}

find_best_arma_order <- function(x) {
  arima.model <- auto.arima(
    x,
    d = 0,
    max.p = 5,
    max.q = 5,
    ic = "aic",
    seasonal = FALSE,
    parallel = TRUE,
    stepwise = FALSE
  )
  
  best.ar.order <- arima.model$arma[1]
  best.ma.order <- arima.model$arma[2]
  
  return(list(ar = best.ar.order, ma = best.ma.order))
}


fit_garch_11_model <- function(x, ar.order, ma.order) {
  garchspec = ugarchspec(
    variance.model = list(garchOrder = c(1, 1)),
    mean.model = list(
      armaOrder = c(ar.order, ma.order),
      include.mean = T
    ),
    distribution.model = "sged"
  )
  
  garch.model <- tryCatch(
    ugarchfit(garchspec, x, solver = 'hybrid'),
    warning = function(w)
      w
  )
  
  return(garch.model)
}

compute_arima_garch_indicator <- function(x) {
  arma_order <- find_best_arma_order(x)
  garch_model <- fit_garch_11_model(x, arma_order$ar, arma_order$ma)
  
  if (is(garch_model, "warning")) {
    window_range <- range(index(x))
    str_interp("Problem encountered in window ${window_range[1]} to ${window_range[2]}\n") %>%
      warning
    
    return(1)
  } else{
   
    arima_garch_indicator <-
      ugarchforecast(garch_model, n.ahead = 1)@forecast$seriesFor %>%
      map_dbl( ~ if_else(.x < 0,-1, 1))
    
    return(arima_garch_indicator)
    
  }
  
}


```
Function to compute the indicator that can be passed to quantstrat:

```{r}
rolling_arima_garch_indicator <- function(x, n = 500, col_name = "daily_return") {
  results <- tk_tbl(x, rename_index = "date") %>%
    tq_mutate(select = col_name,
              mutate_fun = rollapply,
              width = n,
              FUN = compute_arima_garch_indicator,
              col_rename = "arima_garch_indicator"
              ) %>%
    tk_xts(select = "arima_garch_indicator", date_var = "date")
  
  return(results)
  
}

```


Add the indicator to the backtest:

```{r}
add.indicator(
  strategy = strategy.st,
  name = "rolling_arima_garch_indicator",
  arguments = list(x = quote(mktdata),
                   col_name = "daily_return",
                   n = window_size),
  label = "arima_garch_indicator"
)
```

# Signal

Signals for when to go long or short:

```{r}
add.signal(
  strategy = strategy.st,
  name = "sigThreshold",
  arguments = list(
    column = "arima_garch_indicator",
    threshold = 1,
    relationship = "eq"
  ),
  label = "long"
)

add.signal(
  strategy = strategy.st,
  name = "sigThreshold",
  arguments = list(
    column = "arima_garch_indicator",
    threshold = -1,
    relationship = "eq"
  ),
  label = "short"
)
```

# Buy/Sell Rules

```{r}
# buy to open
add.rule(
  strategy = strategy.st,
  name = "ruleSignal",
  arguments = list(
    sigcol = "long",
    sigval = TRUE,
    orderqty = pos_per_signal,
    ordertype = "stoplimit",
    orderside = "long",
    threshold = 0.0005,
    prefer = "Open",
    replace = FALSE,
    osFUN=osMaxPos
  ),
  type = "enter",
  label = "EnterLONG"
)

# sell to open
add.rule(
  strategy = strategy.st,
  name = "ruleSignal",
  arguments = list(
    sigcol = "short",
    sigval = TRUE,
    orderqty = -pos_per_signal,
    ordertype = "stoplimit",
    orderside = "short",
    threshold = 0.0005,
    prefer = "Open",
    replace = FALSE,
    osFUN=osMaxPos
  ),
  type = "enter",
  label = "EnterSHORT",

)

# sell to close
add.rule(
  strategy.st,
  name = "ruleSignal",
  arguments = list(
    sigcol = "short",
    sigval = TRUE,
    orderside = "long",
    ordertype = "market",
    orderqty = "all",
    replace = TRUE 
  ),
  type = "exit",
  label = "Exit2SHORT"
)

# buy to close
add.rule(
  strategy.st,
  name = "ruleSignal",
  arguments = list(
    sigcol = "long",
    sigval = TRUE,
    orderside = "short",
    ordertype = "market",
    orderqty = "all",
    replace = TRUE
  ),
  type = "exit",
  label = "Exit2LONG"
)

```

# Backtest!

```{r}

applyStrategy(strategy.st, portfolios = portfolio.st)
```

```{r}
updatePortf(portfolio.st)
updateAcct(account.st)
updateEndEq(account.st)
```


# Analytics


```{r}
chart.Posn(portfolio.st, subset = paste0(init_date,"/"))
```
```{r}
tstats <- tradeStats(portfolio.st)
tstats %>%
  as_tibble %>%
  pivot_longer(cols = c(-Portfolio, -Symbol), names_to = "metric", values_to = "value") %>%
  mutate_if(is.numeric, round, 2)
```
```{r}
acct <- getAccount(account.st)
xyplot(acct$summary)
```
```{r}
plot(acct$summary$End.Eq, main = "Equity Curve")
```

```{r}
acct$summary$End.Eq %>%
  Return.calculate() %>%
  charts.PerformanceSummary
```

```{r}
PortfReturns(Account = account.st) %>%
  table.AnnualizedReturns()
```

```{r}
PortfReturns(Account = account.st)['2018-12-28/'] %>%
  table.AnnualizedReturns()
```

Compare with buy and hold:

```{r, fig.dim=c(5, 10)}
strat_ret <- PortfReturns(Account = account.st)['2018-12-28/']
bh_ret <- Return.calculate(SPY$adjusted['2018-12-28/'])

names(strat_ret) <- "ARIMA+GARCH"
names(bh_ret) <- "buy and hold"

cbind(strat_ret, bh_ret) %>%
  charts.PerformanceSummary(wealth.index=TRUE)
```
Analysis where strategy screwed up the most:

```{r}
chart.Posn(portfolio.st, subset = '2018-12-28/')
```

```{r}
chart.Posn(portfolio.st, subset = '2019-09-25/2019-10-25')
```

```{r}
chart.Posn(portfolio.st, subset = '2020-02-10/2020-04-25')
```

Sanity check that orders and signals are consistent:


```{r}
mktdata %>%
  tk_tbl(rename_index = "date") %>%
  select(-volume,-adjusted,-daily_return) %>%
  filter(!is.na(arima_garch_indicator))
```


```{r}
book <- getOrderBook(portfolio.st)
book$`Port.ARIMA+GARCH`$SPY %>%
  tk_tbl(rename_index = "Order.SubmitTime") %>%
  select(
    Order.SubmitTime,
    Order.StatusTime,
    Rule,
    Order.Status,
    Order.Qty,
    Order.Price,
    Order.Type,
    Order.Side,
    
  )
```

